Who does big team science?

### 2023-08-29 manuscript_scopus.Rmd
updating manuscript

While publications on the whole are diversifying, we did not yet find
equality in the representation for first/corresponding author spots
versus all other authors. In general, first authors appear to be less
diverse, representing more European and North American authors, while
other authors include more Asian and African authors. These effect sizes
were often small, but the inequality still persists across years, even
if they are slowly decreasing. Diverse teams are more likely to have
papers with stronger "impact" [@freeman2015; @hinnant2012; @jones2008;
@yang2022] with higher citation metrics for more diverse author lists.
The introduction of contributorship models [e.g., CRediT @allen2019]
will hopefully continue to push these effects down, as they highlight
each individual's contribution to a manuscript.

>>>>

While publications on the whole are diversifying, we did not yet find
equality in the representation for first/corresponding author spots
versus all other authors. In general, first authors appear to be less
diverse, representing more European and North American authors, while
other authors include more Asian and African authors. These effect sizes
were often small, but the inequality still persists across years, even
if they are slowly decreasing. Diverse teams are more likely to have
papers with stronger "impact" [@freeman2015; @hinnant2012; @jones2008;
@yang2022] with higher citation metrics for more diverse author lists.
The introduction of contributorship models (e.g., CRediT[@allen2019])
will hopefully continue to push these effects down, as they highlight
each individual's contribution to a manuscript.

### 2023-08-29 manuscript_scopus.tex
updating manuscript

While publications on the whole are diversifying, we did not yet find
equality in the representation for first/corresponding author spots
versus all other authors. In general, first authors appear to be less
diverse, representing more European and North American authors, while
other authors include more Asian and African authors. These effect sizes
were often small, but the inequality still persists across years, even
if they are slowly decreasing. Diverse teams are more likely to have
papers with stronger ``impact''\textsuperscript{59--62} with higher citation metrics for more diverse author lists.
The introduction of contributorship models\textsuperscript{e.g., CRediT 42}
will hopefully continue to push these effects down, as they highlight
each individual's contribution to a manuscript.

>>>>

While publications on the whole are diversifying, we did not yet find
equality in the representation for first/corresponding author spots
versus all other authors. In general, first authors appear to be less
diverse, representing more European and North American authors, while
other authors include more Asian and African authors. These effect sizes
were often small, but the inequality still persists across years, even
if they are slowly decreasing. Diverse teams are more likely to have
papers with stronger ``impact''\textsuperscript{59--62} with higher citation metrics for more diverse author lists.
The introduction of contributorship models (e.g., CRediT\textsuperscript{42})
will hopefully continue to push these effects down, as they highlight
each individual's contribution to a manuscript.
